### 2016-11-05 introduction.tex
more shit

A recently proposed method for compressing recurrent neural networks (\cite{prabhavalkar2016compression}) uses the singular values of a trained weight matrix as basis vectors from which to derive a compressed hidden layer. Some other recent works like \cite{Anders2016quant} have tried successfully to achieve compression through weight quantization followed by an encoding step while others such as \cite{deepcompression2016} have tried to expand on this by adding weight-pruning as a preceding step to quantization and encoding.

In summary, we can say that there are many different ways to improve network generalization by altering the training procedure, the objective error function, or by using compressed representations of the network parameters.

@@

If we wanted to continually shrink a network to its absolute minimal size, we might accomplish this using any number of off-the-shelf pruning algorithms, such as Skeletonization (\cite{mozer1989skeletonization}), Optimal Brain Damage (\cite{lecun1989optimal}), or later variants such as Optimal Brain Surgeon (\cite{hassibi1993second}). In fact, we borrow much of our inspiration from these antecedent algorithms, with one major variation: Instead of pruning individual weights, we prune entire neurons, thereby eliminating all of their incoming and outgoing weight parameters in one go, resulting in more memory saved, faster.

>>>>

A recently proposed method for compressing recurrent neural networks (\cite{prabhavalkar2016compression}) uses the singular values of a trained weight matrix as basis vectors from which to derive a compressed hidden layer. \cite{Anders2016quant} successfully implemented network compression through weight quantization with an encoding step while others such as \cite{deepcompression2016} have tried to expand on this by adding weight-pruning as a preceding step to quantization and encoding.

In summary, we can say that there are many different ways to improve network generalization by altering the training procedure, the objective error function, or by using compressed representations of the network parameters. But these are not, strictly speaking, examples of techniques to reduce the number of parameters in a network. For this we must employ some form of pruning criteria.

@@

If we wanted to continually shrink a network to its absolute minimum possible size, we might accomplish this using any number of off-the-shelf pruning algorithms, such as Skeletonization (\cite{mozer1989skeletonization}), Optimal Brain Damage (\cite{lecun1989optimal}), or later variants such as Optimal Brain Surgeon (\cite{hassibi1993second}). In fact, we borrow much of our inspiration from these algorithms, with one major variation: Instead of pruning individual weights, we prune entire neurons, thereby eliminating all of their incoming and outgoing weight parameters in one go, resulting in more memory saved, faster.
